How Important are Usage Examples in REST API Documentation?

### 2017-03-06 controlled_study.tex
two plots complete

    \begin{axis}[
      axis y line*=right,
      axis x line=none,
      ymin=0, ymax=100,
      ylabel= Success Rate,
      yticklabel={\pgfmathparse{\tick}\pgfmathprintnumber{\pgfmathresult}\%},
      width=2.8in
    ]
    \addplot[dashed,mark=*,gray]
      coordinates{
        (0,0)
        (0.0148,48)
        (0.0295,66)
        (0.0441,66)
        (0.059,45.0)
    }; \addlegendentry{G1 Success Rate}

    \addplot[smooth,mark=*,black]
      coordinates{
        (0,0)
        (0.0148,20)
        (0.0295,10)
        (0.0441,6)
        (0.059,5.0)
    }; \addlegendentry{G2 Success Rate}
    \end{axis}

>>>>

    \begin{axis}[
      axis y line*=right,
      axis x line=none,
      ymin=0, ymax=100,
      ylabel= Success Rate,
      yticklabel={\pgfmathparse{\tick}\pgfmathprintnumber{\pgfmathresult}\%},
      width=2.8in
    ]
    \addplot[dashed,mark=*,gray] table [col sep=comma, x expr=\coordindex, y=SuccessRate] {groupone_success.csv};
    \addlegendentry{G1 Success Rate}

    \addplot[smooth,mark=*,black] table [col sep=comma, x expr=\coordindex, y=SuccessRate] {grouptwo_success.csv};
      \addlegendentry{G2 Success Rate}
    \end{axis}
